Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-26 tex/ms.tex
acks and section structure

\section{Formulating the Model}
\label{sec:model}

%This note, based on the original note from JWR on Feb. 8, 2012, includes revisions from David Hogg, James Long, Nat Butler, and Josh Bloom.

@@

\section{The Light Curve Model}
\label{sec:model}
\subsection{Modeling Non-Detections}
To model the mean brightness of the light curve as a function of time, we use a multiple-harmonic Fourier model with angular oscillation frequency $\omega$,
\begin{eqnarray}\displaystyle
\mu_i' &=& A_0 + \sum_{k=1}^K A_k\, \sin (t_i \, \omega  k) + B_k\, \cos (t_i \, \omega  k)
\quad ,\label{eq:fourier}
\end{eqnarray}
where $\mu_i'$ is the model brightness estimate in magnitude at time $t_i$, $\sqrt{A_k^2 + B_k^2}$ is the amplitude of the $k^{\rm th}$ harmonic of the frequency $\omega$ and $\tan^{-1}(\frac{B_k}{A_k})$ is the relative phase offset of harmonic $k$.  The number of harmonics, $K$, can either be fixed or treated as a free parameter over which to optimize the likelihood.

@@

\acknowledgements It is a pleasure to thank Josh Bloom (Berkeley) for
valuable discussions and comments.  Partial support for this project
was provided by [JWR: PUT GRANT NUMBERS HERE], NASA grant NNX12AI50G,
and NSF grant IIS-1124794.

>>>>

\section{The Model}
\label{sec:model}

@@

\subsection{Modeling Non-Detections}
To model the mean brightness of the light curve as a function of time, we use a multiple-harmonic Fourier model with angular oscillation frequency $\omega$,
\begin{eqnarray}\displaystyle
\mu_i' &=& A_0 + \sum_{k=1}^K A_k\, \sin (t_i \, \omega  k) + B_k\, \cos (t_i \, \omega  k)
\quad ,\label{eq:fourier}
\end{eqnarray}
where $\mu_i'$ is the model brightness estimate in magnitude at time $t_i$, $\sqrt{A_k^2 + B_k^2}$ is the amplitude of the $k^{\rm th}$ harmonic of the frequency $\omega$ and $\tan^{-1}(\frac{B_k}{A_k})$ is the relative phase offset of harmonic $k$.  The number of harmonics, $K$, can either be fixed or treated as a free parameter over which to optimize the likelihood.

@@

\acknowledgements It is a pleasure to thank
%
  Josh Bloom (Berkeley) and
  Nat Butler (ASU)
%
for valuable discussions and comments.
%
Partial support for this project was provided by \hogg{[JWR: PUT GRANT
  NUMBERS HERE]}, NASA grant NNX12AI50G, and NSF grant IIS-1124794.
